---
title: "Linear models and cross-validation"
output: html_document
---

Loading data

```{r}
df <- read.csv("/home/rauf/Programs/semester_2/stat-learn/ha_1/Advertising.csv")
ind <- df$X
df <- df[, -1]  
head(df)
```

Visualisation for better intuition
```{r, message=F, warning=F}
library(PerformanceAnalytics)
chart.Correlation(df)
```

Is there a relationship between advertising sales and budget?
```{r}
lm.lazy.fit = lm(Sales~., data=df)
summary(lm.lazy.fit)
```
F-statistic in Table is very low, indicating
clear evidence of a relationship between advertising and sales.
The p-values for TV and radio are low,
but the p-value for newspaper is not. This suggests that only TV and
radio are related to sales.

How accurately can we predict future sales?
```{r}
confint(lm.lazy.fit)
```

The VIF scores are close to 1, suggesting no evidenceof collinearity.
```{r}
library(car)
vif(lm.lazy.fit)
```

Is the relationship linear?
```{r}
par(mfrow = c(1, 2))
plot(predict(lm.lazy.fit), residuals(lm.lazy.fit))
plot(predict(lm.lazy.fit), rstudent(lm.lazy.fit))
```

The additive assumption may be unrealistic for data set. Trend is in a residual plot suggests presence of non-additive relationships.

Lets check by adding interaction term.
```{r}
lm.interacion.fit = lm(Sales~TV*Radio + Newspaper, data=df)
summary(lm.interacion.fit)
```
A small p-value associated with the interaction term indicates the presence of such
relationships. 


We also observe large p-valuse associated with the Newspaper term. Lets try to get rid of it
```{r}
lm.shrinked.fit = lm(Sales~TV*Radio, data=df)
summary(lm.shrinked.fit)
```

Simple cross-validation function
```{r}
cv.lm <- function(df, formula, nchuncks) {
    df.size <- dim(df)[1]
    ind.perm <- sample(ind, df.size, replace = F)
    chunk.size <- df.size / (nchuncks + 1)
    splitted <- split(ind.perm, ceiling(ind/chunk.size))
    test.set <- splitted[1][[1]]
    train.chunks <- splitted[-1]

    err.on.chunk <- function(chunk) {
        chunk <- chunk[[1]]
        model <- lm(formula, data=df[chunk, ])
        pred <- predict(model, df[test.set, ])
        y <- df$Sales[test.set]
        sum((y - pred) ^ 2) / length(y)
    }

    errors <- numeric(nchuncks)
    for (i in 1:nchuncks) {
        errors[i] <- err.on.chunk(train.chunks[i])
    }
    print(formula)
    cat("Error mean = ", mean(errors))
    cat("\tError sd = ", sd(errors))
    cat("\n")
}
```

Now let's try it out
```{r}
nchunks <- 10
cv.lm(df, formula(Sales ~ ., data = df), nchunks)
cv.lm(df, formula(Sales~TV + Radio, data = df), nchunks)
cv.lm(df, formula(Sales~TV*Radio, data = df), nchunks)
```

