---
title: "Home assigntment #1"
output: html_document
---

Loading data

```{r}
df <- read.csv("/home/rauf/Programs/semester_2/stat-learn/ha_1/Advertising.csv")
set <- df$X
df <- df[, -1]  
head(df)

training.set <- sample(set, size = length(set)*0.7)
test.set <- set[-training.set]
df.train <- df[training.set,]
df.test <- df[test.set,]

```

Visualisation for better intuition
```{r, message=F, warning=F}
library(PerformanceAnalytics)
chart.Correlation(df.train)
```

Is there a relationship between advertising sales and budget?
```{r}
lm.lazy.fit = lm(Sales~., data=df.train)
summary(lm.lazy.fit)
```
F-statistic in Table is very low, indicating
clear evidence of a relationship between advertising and sales.
The p-values for TV and radio are low,
but the p-value for newspaper is not. This suggests that only TV and
radio are related to sales.

How accurately can we predict future sales?
```{r}
confint(lm.lazy.fit)
```

The VIF scores are close to 1, suggesting no evidenceof collinearity.
```{r}
library(car)
vif(lm.lazy.fit)
```

Is the relationship linear?
```{r}
par(mfrow = c(1, 2))
plot(predict(lm.lazy.fit), residuals(lm.lazy.fit))
plot(predict(lm.lazy.fit), rstudent(lm.lazy.fit))
```

The additive assumption may be unrealistic for data set. Trend is in a residual plot suggests presence of non-additive relationships.

Lets check by adding interaction term.
```{r}
lm.interacion.fit = lm(Sales~TV*Radio + Newspaper, data=df.train)
summary(lm.interacion.fit)
```
A small p-value associated with the interaction term indicates the presence of such
relationships. 


We also observe large p-valuse associated with the Newspaper term. Lets try to get rid of it
```{r}
lm.shrinked.fit = lm(Sales~TV*Radio, data=df.train)
summary(lm.shrinked.fit)
```

Now lets compare predictions by different models on test set
```{r, message=F}
library(rminer)
lm.lazy.predict <- predict(lm.lazy.fit, df.test)
mmetric(y = df.test$Sales, x = lm.lazy.predict, metric = 'R2')
```

```{r}
lm.interacion.predict <- predict(lm.interacion.fit, df.test)
mmetric(y = df.test$Sales, x = lm.interacion.predict, metric = 'R2')
```

```{r}
lm.shrinked.predict <- predict(lm.shrinked.fit, df.test)
mmetric(y = df.test$Sales, x = lm.shrinked.predict, metric = 'R2')
```